Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-26 concl.tex
editing
putting it in Phys Rev E Format
various small changes
see previous commit

\section{ Conclusions \& Future Work}\label{sec:conc}

\begin{enumerate}
\item  This need to be rewritten to conclude and address this paper...
\end{enumerate}

>>>>

\section{ Conclusions \& Future Work }\label{sec:conc}
{\color{red} NOT EDITABLE}
\begin{enumerate}
\item  This need to be rewritten to conclude and address this paper...
\end{enumerate}

Paragraph about PE as regime-shift detection.  Here's some text that
we had in a footnote in the methods section, which no longer talks
about regimes or regime-shift detection: It should be noted that
[[non-weighted?  non-windowed?]]  permutation entropy has been used to
detect seizures in brainwave data \cite{cao2004det}, which can be
viewed as regime detection.  The purpose of this paper is \emph{not}
to rigorously explore regime detection but to explore quantifying
complexity of a time series.
